Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-01 paper.qmd
Added langevitour for model fit with tSNE

```{r}
#| eval: false
df_model_data_two_curvy_filtered <- bind_rows(true_model_two_curvy, data_two_curvy)

@@

>>>>

```{r}
#| label: langevitour-true-two-curvy-proj
#| eval: false
df_model_data_two_curvy_filtered <- bind_rows(true_model_two_curvy, data_two_curvy)

@@

```{r}
#| label: langevitour-best-fit-two-curvy-proj-tsne
#| eval: false

df_model_data_two_curvy_filtered <- bind_rows(df_bin_two_curvy, data_two_curvy)

langevitour::langevitour(df_model_data_two_curvy_filtered[1:(length(df_model_data_two_curvy_filtered)-1)],
                         lineFrom = distance_df_small_edges_two_curvy$from,
                         lineTo = distance_df_small_edges_two_curvy$to,
                         group = factor(df_model_data_two_curvy_filtered$type,
                                        c("data", "model")),
                         levelColors = c(clr_choice, "#000000"))
```
